---
title: "Description and usage of SpectraMapping"
output:
    BiocStyle::html_document:
        toc_float: true
vignette: >
    %\VignetteIndexEntry{Description and usage of SpectraMapping}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
    %\VignettePackage{Spectra}
    %\VignetteDepends{Spectra,BiocStyle}
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Package**: `r Biocpkg("SpectraMapping")`<br />
**Authors**: `r packageDescription("SpectraMapping")[["Author"]] `<br />
**Last modified:** `r file.info("SpectraMapping")$mtime`<br />
**Compiled**: `r date()`

```{r, echo = FALSE, message = FALSE}
library(Spectra)
library(BiocStyle)
```

# Introduction

The `Spectra` package provides a central infrastructure for the
handling of Mass Spectrometry (MS) data. The package supports
interchangeable use of different *backends* to import MS data from a
variety of sources (such as mzML files). The `SpectraMapping` package
allows the import and mapping of MS/MS data from and to different formats.
This vignette illustrates the usage of the `SpectraMapping`
package.

# Importing MS/MS data from files

Files store one to multiple spectra, typically centroided and of
MS level 2. In our short example below, we load a file which is
provided with this package. Below we first load all required packages
and define the paths to the files.

```{r load-libs}
library(Spectra)
library(SpectraMapping)
library(furrr)
library(devtools)


```

MS data can be accessed and analyzed through `Spectra` objects. Below
we create a `Spectra` with the data from these files. To this end
we provide the file names and specify to use a `MsBackendMapping()`
backend as *source* to enable data import.

```{r import}

plan(multiprocess)
sp <- Spectra(
  system.file("test_spectra/sample.mgf", package="SpectraMapping"),
  source = MsBackendMapping(format = MsFormatMgf(parallel=TRUE)))

```

With that we have now full access to all imported spectra variables
that we list below.


```{r spectravars}
spectraVariables(sp)
```

Besides default spectra variables, such as `msLevel`, `rtime`,
`precursorMz`, we also have additional spectra variables such as the
`title` of each spectrum in the file.

```{r instrument}
sp$rtime
sp$title
```

In addition we can also access the m/z and intensity values of each
spectrum.

```{r mz}
mz(sp)
intensity(sp)
```


```{r}
sessionInfo()
```
